PAMELA: an annotation-based Java Modeling Framework

### 2021-02-02 1-Main.tex
LOW / Test
work on architecture and process (AB)
(bugfix) remove a link in order to be able to compile

%\usepackage[colorinlisttodo]{todonotes}

@@

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2https://www.overleaf.com/project/5efee0e8ad6bc10001d47854
}

@@

@@

\section{Approach}
\label{sec:pamproc}
\input{pamelaProcess.tex}

@@

% Prout

>>>>

\usepackage{todonotes}

@@

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

% DRAFT
\newcommand{\ab}[1]{{\color{blue} #1}} % draft mode

@@

\section{Approach and Development Process}
\label{sec:pamproc}
\input{pamelaProcess.tex}

@@

% Test
